Asymmetric functional prediction bands for assessing the validity of spatiotemporally smooth biomechanical curve data

### 2021-08-06 paper.Rmd
Get paper.Rmd to compile

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v1 <- crossval_coverage(data, floa, floa.point, method = "all", ver = "v1")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v2 <- crossval_coverage(data, floa, floa.point, method = "all", ver = "v2")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v3 <- crossval_coverage(data, floa, floa.point, method = "all", ver = "v3")

>>>>

```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v1")
floa.point <- floa_point(data)

cover.cross.v1 <- crossval_coverage(data, floa, floa.point, method = "all")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v2")
floa.point <- floa_point(data)

cover.cross.v2 <- crossval_coverage(data, floa, floa.point, method = "all")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v3")
floa.point <- floa_point(data)

cover.cross.v3 <- crossval_coverage(data, floa, floa.point, method = "all")
